%\documentclass{report}
%\usepackage{setspace}
%\begin{document}
\newpage
% \pagestyle{empty}
%  \thispagestyle{empty}
% %\topmargin=10pt
% \pagenumbering{roman}
% \setcounter{page}{0}
\addcontentsline{toc}{section}{Title Page}
\vskip -5em  
%\hskip 2em
\begin{center}
  {\singlespace \uppercase{\bf Text Encapsulation: Summarization to the minimum } \par} 
  \vskip 2em 
  {\lineskip 1.3em
    \begin{tabular}[t]{c} by\\ \\ Imran Ali
    \end{tabular}\par} 
        
    \vskip 5.6em 
\singlespace A research submitted in fulfillment of the requirements for the \\ degree of Masters of Sciences in \\
  Computer Science

\vskip 5em    
\vskip 0.5em
{\singlespace 
\begin{center}
\begin{tabular}{rl}

 \\[-1em]
Advisor:   & Dr.\ Sumanta \ Guha (Chairperson)  \\[-0.8em]
	   & Professor.\ Phan \ Minh \ Dung  \\ [-0.8em] 
	   & Dr.\ Paul \ Janecek \\[-0.8em]\\[-0.8em] \\ \\
					
%\end{tabular}					
%\begin{tabular}{ll}					
              Nationality:  & Pakistani \\[-0.8em]
Previous Degree:  & Masters of Computer Science\\[-0.8em]
				  & University of Balochistan \\[-0.8em]
%				  & Institute of Science and Technology\\[-0.8em]
				  & Quetta, Pakistan\\
        		  
Scholarship Donor: &University of Balochistan Quetta, Pakistan - AIT Fellowship\\		

\end{tabular}
\end{center}
\vskip 3.0em       
\centerline{}
\vskip 2em 
}  
\end{center}
\begin{center}
\singlespace Asian Institute of Technology\\School of Engineering and Technology\\Thailand\\August 2010
\end{center}
 \vfill


\pagestyle{plain}
%\topmargin=10pt
\pagenumbering{roman}
\setcounter{page}{1}
\newpage\pagestyle{plain}
\addcontentsline{toc}{section}{Acknowledgement}
\onecolumn                  % Single-column.
\if@twoside\else\raggedbottom\fi % Ragged bottom unless twoside option.

\begin{center}
{\bf Acknowledgement\\ } %\vskip 1em
% \vskip 1em
\end{center}
\singlespace
%\doublespace 
\hspace{8.5mm}

Glory be to Allah, the Creator of the universe, who blessed me with kind parents, knowledgeable mentors and sincere friends who have continually assisted me 
in achieving success throughout my career.

I am grateful to my advisor Dr. Sumanta \ Guha who has taught me the process of research. I would like to extend my gratitude to Prof. P.M. Dung and 
Dr. Paul Janecek for their valuable views and suggestion to understand and improve my work. 

\vspace{3mm}
I am thankful to Mr.\ Suresh \ Pokharel who assisted me in identifying relevant online sources. I am also thankful to Mr. \ Abdul \ Basit who guided me
in report writing. 

\vspace{3mm}
I would like to thank my scholarship donor, The University of Balochistan, for providing me this opportunity and supporting me financially. 

\newpage
\pagestyle{plain}
\addcontentsline{toc}{section}{Abstract}
%  \begin{abstract}

\onecolumn                  % Single-column.
\if@twoside\else\raggedbottom\fi % Ragged bottom unless twoside option.

\begin{center}
{\bf Abstract\\ \vskip 1em}
\vskip 1em
\end{center}
\doublespace
\singlespace %\hspace{8.5mm}
% \vspace{-1em}
Understanding text and producing a concise representation of it has been a challenging task both for humans and automated systems. Information overload 
necessitates the development of accurate extractive systems. Many extractive summarization systems have been proposed and developed to summarize text, my work is focused on 
producing a single sentence summary on a higher level consisting of least possible words containing essential grammatical phrases 
i.e. subject, verb, and object to encapsulate the information. 



\setlength{\parskip}{0pt}
\newpage
\addcontentsline{toc}{section}{Table of Contents}
\tableofcontents


 \newpage
 \addcontentsline{toc}{section}{List of Tables}
 \listoftables

%===================== List of Figures ======================
\newpage
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

\setlength{\parskip}{12pt} % \clearpage ends the page, and also dumps out all floats. 
%\end{document}
